### 2019-04-08 manuscript.tex
Update manuscript.tex

% \cite{Koom14}: `` practices of female excision are so diverse that they may defy generalizable remedies"  ``Rather than relying on common campaign models, transferable advocacy tools, or `best practices,' scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics."

@@

%\{cf: a few words on each nation's FGC policy}
% read \cite{MohaHass14, MuteMill16, PashPonn16, VaroFras14}

A multicultural egalitarian approach respecting both cultural identity and basic legal human rights was addressed \cite{BoylCarb10, Wade11}.  Instead of straightforward campaigns against traditional culture, "culturalconstestaion" characterized by politicized negotiation and, at times, resistance, was proposed. \cite{Koom14}.

@@

%\cfcmt{Bicchieri's norm theory—
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do
\cite{Bicc06}
First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cfcmt{normative norm?}
and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.  Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cfcmt{empirical norm?}?

% attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
\cite{UNFPA14, UNIC16}
\subsection{suggestions and Limitations}\label{suggestions-and-Limitations}

@@

% Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).

@@

% \cite{Meye00}:  rational model vs. hierarchical identification model; and plus oppression social context.  That is, knowing ≠ abling ≠ wanting ≠ doing.  How to apply this concept to theories of feminist/gender, modernization and convention.

>>>>

% \cite{Koom14}: `` practices of female excision are so diverse that they may defy generalizable remedies"  ``Rather than relying on common campaign models, transferable advocacy tools, or `best practices,' scholars and anti-FGM activists must rethink female excision in terms of its diverse contextual meanings and its dynamic global politics."  Instead of straightforward campaigns against traditional culture, "culturalconstestaion" characterized by politicized negotiation and, at times, resistance, was proposed. \cite{Koom14}.

A multicultural egalitarian approach respecting both cultural identity and basic legal human rights was addressed \cite{BoylCarb10, Wade11}.

@@

% read \cite{MohaHass14, MuteMill16, PashPonn16, VaroFras14}

@@

%\cfcmt{Bicchieri's norm theory \cite{Bicc06}:
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do

% attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
\cite{UNFPA14, UNIC16}

@@

@@
